\documentclass{article}
% Change "article" to "report" to get rid of page number on title page
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{algorithmic,algorithm}
\usepackage{setspace}
\usepackage{Tabbing}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul,color}
\usepackage{ulem}
\usepackage{graphicx,float,wrapfig}
\usepackage{amsfonts}
\usepackage{pifont}
\usepackage{booktabs}
\usepackage{hyperref}

\newcommand{\tickYes}{\checkmark}
\newcommand{\tickNo}{\hspace{1pt}\ding{55}}

% In case you need to adjust margins:
\topmargin=-0.45in      %
\evensidemargin=0in     %
\oddsidemargin=0in      %
\textwidth=6.8in        %
\textheight=9.4in       %
\headsep=0.25in         %

% Homework Specific Information
\newcommand{\hmwkTitle}{Project\ \#4}
\newcommand{\hmwkDueDate}{Nov.\ 1,\ 2010}
\newcommand{\hmwkClass}{Cloud Computing}
\newcommand{\hmwkClassTime}{MW\ 4:10-5:25pm}
\newcommand{\hmwkClassInstructor}{Keke\ Chen}
\newcommand{\hmwkAuthorName}{Shumin\ Guo}

% Setup the header and footer
\pagestyle{fancy}                                                       %
\lhead{\hmwkAuthorName}                                                 %
\chead{\hmwkClass\ - \hmwkTitle}  %
\rhead{Page\ \thepage\ of\ \pageref{LastPage}}                          %
\lfoot{\lastxmark}                                                      %
\cfoot{}                                                                %
\rfoot{}                          %
\renewcommand\headrulewidth{0.4pt}                                      %
%\renewcommand\footrulewidth{0.4pt}                                     %

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Make title
\title{\textbf{\hmwkClass:\ 
      \hmwkTitle}\\\normalsize\small{Due\ Date:\
    \hmwkDueDate}} 
\date{\today}
\author{\textbf{\hmwkAuthorName}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\begin{center}
\textbf{CS499/699 Cloud Computing Mini \\
Project 4: Hacking Hadoop on EC2}
\end{center}

\textbf{Goals:} We will learn to use EC2 and S3 and setup hadoop on EC2 with
scripts. 
 
This project consists of two parts: the first part is getting familiar
with EC2 and S3. The second part is hacking existing scripts and
setting up hadoop on EC2 and using S3 as the persistent storage for
hadoop.
 
Note: EC2 tools have been installed at nimbus17 /usr/local/ec2. Boto
python library has been installed, too.
 
\textbf{Steps:}

\underline{First part:}
 
review the lecture about using AWS and create your own AWS account
online by yourself. Ask me for your AWS coupon code and redeem it
(there is an option in your AWS account).
 
login to your nimbus17 account and setup the environment variables for
AWS, especially your AWS ID and keys.
 
Follow the steps we discussed in class to start an EC2 instance and to
use S3, with both EC2 tools and boto library.

\underline{Second part:}
 
Read the tutorial http://wiki.apache.org/hadoop/AmazonEC2 for setting
up hadoop on EC2 using the existing scripts (you will realize they
won’t work well). Read 
\begin{verbatim}
http://www.michael-noll.com/wiki/Running_Hadoop_On_Ubuntu_Linux_(Single-Node_Cluster)  
\end{verbatim}
and related links on how to configure a hadoop system (note the
difference between version 0.19 and 0.20. For version 0.19, everything
is in the same configuration file: hadoop-site.xml.)
 
Copy the HadoopEC2 tool directory from the directory
/usr/local/hadoop/src/contrib/ec2/ to your own directory, e.g.,
~/ec2/. Go to ~/ec2/bin and start a hadoop cluster with hadoop-ec2
script with 1 data node. Use ec2-describe-instances to find the
external ip and internal ip for the instances.
 
Login the master node and check how the cluster is running. You can
use hadoop fsck / to check the status. You will find the number of
data nodes is 0, which is abnormal. You can check the log files at
/mnt/hadoop/logs to see what happened.
 
Read the scripts in the directory ~/ec2/ and try to answer the
following questions\\

(1) How do you pass a script file to an EC2 instance, when you start
up an instance?  (2) After an instance is started, how to pass a
command or a script and execute it in the instance?  (3) Check the
file hadoop-ec2-init-remote.sh and describe what the script does for
master node and data node, respectively
 
Consider the possible reasons that the hadoop cluster does not
normally. Write down what you observed and analyze the problem. You
may need to check
\begin{verbatim}
 http://www.michael-noll.com/wiki/Running_Hadoop_On_Ubuntu_Linux_(Single-Node_Cluster)
\end{verbatim}
and see a normal process.  (1) does the master node work normally in
the single node mode? Are the processes: namenode, jobtracker and
secondary namenode started normally?  (2) can the data nodes
communicate with the master node with keyless ssh? If not, how do you
change the HadoopEC2 script?  (3) are the processes: datanode and
tasktracker in the data node started normally? If not, what is the
reason? You may check whether all the ports are correctly authorized.
 
Revise the scripts and make the hadoop cluster work normally.
 
Read the tutorial http://wiki.apache.org/hadoop/AmazonS3 for using
hadoop with S3. How do you change the configuration in the
corresponding HadoopEC2 script file correspondingly to make the hadoop
input/output based on S3?
 
Check the script cmd-hadoop-cluster and learn how to submit a command
to the cluster. Upload the input data to S3. Submit your project 2
code to a running cluster with input/output set to S3. Write down the
script for submitting the job to the cluster.
 
\textbf{Deliverables:}

You should submit a report that answers the questions at
step 7, 8, 10 and 11, and the zipped working hadoopEC2 scripts to the
WebCT submission system.  You can also try to implement the scripts
with python and the boto library.
 
Remember each time after you finish your experiment, you should check
the EC2 instances and terminate all running ones. Otherwise, it will
keep charging your account.
 
Write a description on what you did, the problems you encountered, and
the result on S3. You can save it on your directory and let me know
the directory.
 
\end{document}