\documentclass[12pt]{article}
% Change "article" to "report" to get rid of page number on title page
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{setspace}
\usepackage{Tabbing}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul,color}
\usepackage{titlesec}
\usepackage{graphicx,float,wrapfig}
\usepackage{url}

% In case you need to adjust margins:
\topmargin=-0.45in      %
\evensidemargin=-1in     %
\oddsidemargin=0in      %
\textwidth=7in        %
\textheight=9.0in       %
\headsep=0.25in         %

% Start of document. 
\begin{document}
\begin{center}                  % Header of file. 
\textbf{Security of Outsourcing of Association Rule Mining - Review} \\ 
\small\textsc{Shumin Guo} \\
\end{center}
% problem identification 
\section*{Problem Description}

Outsourcing transactional data for association rule mining has the
requirement of protecting sensitive data and sensitive association
rules. This paper proposes an algorithm to deal with this problem.  

\section*{Contribution of this paper}
This paper has proposed a secure encryption scheme based on one-to-n
substitution encryption and transforms sensitive transactions
non-deterministically, while at the same time, correct decrytion is
guaranteed. Comprehensive formal analysis is given about the enhanced
one-to-n encryption algorithm including the decrytion guarantee. In
the proposed algorithm, fake items are added to increase the
difficulty of breaking the ciphers. Also, this paper defines
algorithms to recover association from the encrpyted rules and the
computational complexity is analyzed. 

The author also suggested parameters to control the complexity by
controlling the length of fake items and the mapping. And experimental
results show that the proposed algorithm is efficient. 

% weakness description. 
\section*{Weaknesses of this paper}
The security analysis can be a little more comprehensive. 
No discussion about attacking sensitive association rules is given in
the paper. 
 
\end{document} 