\documentclass[12pt]{article}
% Change "article" to "report" to get rid of page number on title page
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{setspace}
\usepackage{Tabbing}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul,color}
\usepackage{titlesec}
\usepackage{graphicx,float,wrapfig}
\usepackage{url}

% In case you need to adjust margins:
\topmargin=-0.45in      %
\evensidemargin=-1in     %
\oddsidemargin=0in      %
\textwidth=7in        %
\textheight=9.0in       %
\headsep=0.25in         %

% Start of document. 
\begin{document}
\begin{center}                  % Header of file. 
\textbf{\large{Project ideas}} \\ 
\small\textsc{Shumin Guo} \\
\end{center}

\begin{enumerate}

\item Implement the data reconstruction algorithms and repeat the
experiments in “limiting privacy breaches in privacy preserving data
mining”, i.e., paper 15. Then, if we change the distribution
assumptions on original data and noise, how effective are the
different methods, particularly the Bayes method? 

References: 13,15
 
\item Compare additive perturbation, random projection perturbation, and
geometric data perturbation, on a few experimental
datasets. Investigate the relationship between the loss of privacy and
the model accuracy. Will random projection perturbation and geometric
data perturbation preserve the accuracy of decision tree classifier?
Will the additive perturbation method preserve the accuracy of
distance-based classifiers, such as k-nearest-neighbor classifier? 

References: 10,20,21
 
\item Compare l-diversity, t-closeness and k-anonymity, and study how data
utility is sacrificed in each model (use decision tree for
experiments) 
 
References: 39,53
 
\item Simulate graph structures (paper 182), and implement the attacks on
graph structure in paper 167. 

References: 167, 182
 
\item Study the social network data publishing problem. Pick one of the
papers 163-166 

References: 163-166
 
\item Study the location privacy problem, and implement algorithms and
repeat some experiments in the paper 175 

References: 170,173,174, 175
 
\item Study the high-dimensional data perturbation problem

References: 29,51,64
 
\item Consider secure outsourced data for k-nearest neighbor search services.

References: 187,189,190,191 

\end{enumerate}

\end{document}