\documentclass[12pt]{article}
% Change "article" to "report" to get rid of page number on title page
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{setspace}
\usepackage{Tabbing}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul,color}
\usepackage{titlesec}
\usepackage{graphicx,float,wrapfig}
\usepackage{url}

% In case you need to adjust margins:
\topmargin=-0.45in      %
\evensidemargin=-1in     %
\oddsidemargin=0in      %
\textwidth=7in        %
\textheight=9.0in       %
\headsep=0.25in         %

% Start of document. 
\begin{document}
\begin{center}                  % Header of file. 
\textbf{\LARGE{Privacy Preserving Computing Project Proposal}} \\ 
\small\textsc{Shumin Guo} \\
\end{center}

% problem identification 
\section*{Study about Addtive and Multiplicative Data Perturbation}
\subsection*{Basic Tasks}
\begin{enumerate}
\item Simulate the addtive perturbation method with regard to decision
  tree classification applications. 
\item Study the distance preservation property of rotation
  perturbation and random perturbation methods.
\item Simulate the application of multiplicative perturbation methods
  w.r.t. k-means clustering algorithm. 
\end{enumerate}

\textbf{Estimated Time: } one week. (02/07/2011 - 02/13/2011)

\subsection*{A Little More Detailed Study}
\begin{enumerate}
\item Study factors that are related to the performance of the addtive
  perturbation method - correlation among attributes. 
\item Study the correlation between privacy and utility for both
  addtive and multiplicative perturbation methods. 
\end{enumerate}

\textbf{Estimated Time: } two weeks. (02/14/2011 - 02/27/2011)

\subsection*{Study on attacks}
\begin{enumerate}
\item Study ICA method for data reconstructruction from perturbed
  data. 
\item Study attacks on random rotation perturbation. 
  - Naive estimation reconstructruction. \\
  - ICA based attack  \\ 
  - Distance inference attack.
\item Study why geometric perturbation can combat attacks addressed by
  previous one. 
\item Study ICA\_based attack about the random perturbation method. 
\end{enumerate}

\textbf{Estimated Time: } two weeks. (02/28/2011 - 03/12/2011)

\end{document} 