\documentclass[12pt]{article}
% Change "article" to "report" to get rid of page number on title page
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{setspace}
\usepackage{Tabbing}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul,color}
\usepackage{titlesec}
\usepackage{graphicx,float,wrapfig}
\usepackage{url}

% In case you need to adjust margins:
\topmargin=-0.45in      %
\evensidemargin=-1in     %
\oddsidemargin=0in      %
\textwidth=7in        %
\textheight=9.0in       %
\headsep=0.25in         %

% Start of document. 
\begin{document}
\begin{center}                  % Header of file. 
\textbf{\large{On Privacy Preserving of Text and Sparse Binary Data
    with Sketches - Review}} \\ 
\small\textsc{Shumin Guo} \\
\end{center}
% problem identification 
\textbf{Problem Description}

Text and binary data has the property of sparsity, which means that
only very few attributes of a data tuple have non-null values, and high
dimensionality, which renders existing privacy preservation methods
ineffective. These properties make existing algorithm about privacy
preservation not be directly used into these types of data. So,
how to effectively preserve privacy for text and binary sparse data
becomes a research problem.

% contribution description. 
\textbf{Contribution of this paper}

This paper proposes a sketch based method for privacy protection of
text and sparse binary data. This method reduces the high dimension to
a lower one by aggregating(sketching) data tuple using a binary random
matrix. By controlling the dimension of the sketch matrix, we can
achive an expected anonymous privacy level. Experiments with the
proposed method show that we can get a good balance between the
utility over classification and clustering algorithms and the privacy.

% weakness description. 
\textbf{Weaknesses of this paper}

As the title of this paper says, text and sparse binary data are the
supposed data type for the sketch method, but this is not very
clearly modeled in the paper. 

For the experiment part, it will be better if the author makes a
comparison between the performance of the existing methods, such as
k-anonymity, and the sketch based method. 

Although this paper has discussion about controlling the dimension of the
sketched data set, and prove that the level of anonymity can be
controlled by adjusting the dimension of the sketch matrix, there is
no discussion about how the dimension and the level of sparsity can
affect the performance of the sketch algorithm. 

Still, this paper fails to point out the property of data mining
algorithms that can be used over the sketched data. 

Are there any possible attacks to the sketched data set? 
 
\end{document} 