\documentclass[16pt]{report}
% Change "article" to "report" to get rid of page number on title page

% In case you need to adjust margins:
% \topmargin=-0.45in      %
% \evensidemargin=-1in     %
% \oddsidemargin=0in      %
% \textwidth=5in        %
% \textheight=9.0in       %
% \headsep=0.25in         %

\begin{document}
\textbf{\Large{A correlation-aware data placement strategy for
    key-value stores}} \\ 

% Problem descriptions.  
\textbf{Problem description}

Large volume of social networking data requires an efficient storage
scheme that is both scalable and can meet the availability
requirements of read intensive access. This paper is trying to make an
attempt to design a key-value storage scheme that can solve this
problem. 

\textbf{Contributions}

The contribution is hard to figure out, as a lot of literature papers
out there have been trying to solve this problem with similar
methods. While in this paper, the author doesn't explain in detail what
has been done by literature papers. Although the author is trying to
claim that the correlation-aware data placement strategy and load
balancing strategy among distributed nodes is novel, it is possible
not (in fact it is not as far as I know). 

\textbf{Defects of this paper}

Generally, this paper is a poorly written one, not only in the content
but also technically. There are tons of syntax errors, which make it
hard to understand what the author is trying to explain. And there are no
concrete examples for explanations. And the type setting of some part
of this paper is not very professional. 

% Final rating score. 
\textbf{Final Rating}
Sadly, I can only give a score between 1.5 and 1.99 over 5. 

\end{document} 